---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This Github repository includes functions to automate sending emails to the weekly seminar speakers and the audience. 

You can set this up once at the beginning of the semester and forget about sending an announcement / reminder throughout the semester !


To use these functions, you should install relevant packages. The code file calls the following R packages.

```{r, eval=FALSE}
library(taskscheduleR) ### use taskscheduleR on Windows, use cronR on Mac
library(gmailr)
library(googlesheets4)
library(rstudioapi)
```

Next, you should set up Gmail API to allow R to access your gmail account. You should read instructions in the following website. 

https://github.com/r-lib/gmailr

Finally, you should set basic parameters in setGmailConfig.R code file.
I recommend creating the seminar schedule table and one-to-one meeting signup table on Google spreadsheet.

The code will read google spreadsheets and retrieve the seminar schedule information.

The code is automated to run on the same day every week, and if there is no seminar scheduled within the next seven days, the code will skip sending the emails in that week.


